---
title: "Openskyr: basic usage"
author: "Luis Gasco Sanchez"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Openskyr: basic usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r setup , include=FALSE }
NOT_CRAN <- identical(tolower(Sys.getenv("NOT_CRAN")), "true")
knitr::opts_chunk$set(purl = NOT_CRAN)
```



This is just a small vignette to show how to load and run openskyr functions. In the future, I will include a shiny app to show the capabilites of the library to display real-time flight data. You have to consider that if you want to test the library with these commands, you will need to provide your own credentials (username/passwords) and probably need to change the time parameters of the functions since there are some [time limitations](https://opensky-network.org/apidoc/rest.html#limitations) in the API, and when you run the functions those data will probably not be accessible anymore.

## Load the library
```{r}
library(openskyr)
```

## Get state vectors
Retrieve any state vector of the OpenSky data without authentication:
```{r, eval=F  }
state_vectors_df <- get_state_vectors()
```

Retrieve any state vector of the OpenSky data with authentication (you need to register in opensky-network):
```{r, eval=F }
state_vectors_df <- get_state_vectors(username="your_username",password="your_password")
```

## Get airport data
Retrieve flights for a certain airport which departed within a given time interval [begin, end]:
```{r eval = F}
data_airport_df <- get_airport_data(username="your_username",password="your_password",
                                     option="departures",airport="EDDF",
                                     begin=1517227200,end=1517230800)
```


## Get flights data
Retrieve flights for a particular aircraft within a certain time interval:
```{r eval = F}
data_specific_flight <- get_flights_data(username="your_username",password="your_password",
                                         icao24="3c675a",begin=1517184000,end=1517270400)
```

Retrieves flights for a certain time interval [begin, end]:
```{r eval = F}
data_all_flight <- get_flights_data(username="your_username",password="your_password",
                                    begin=1517227200,end=1517230800)
```


## Get tracks data
Retrieve the trajectory for a certain aircraft at a given time:
```{r eval = F}
data_flight_track <- get_track_data(username=username,password="your_password",
                                    icao24="494103",time=1587126600)
```



