---
title: "Openskyr: basic usage"
author: "Luis Gasco Sanchez"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Openskyr: basic usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r, setup, include=FALSE }
NOT_CRAN <- identical(tolower(Sys.getenv("NOT_CRAN")), "true")
knitr::opts_chunk$set(purl = NOT_CRAN)
```



This is just a small vignette to show how to load and execute functions from openskyr. In the future, I will include a shiny app to show the capabilites of the library to show airflights real-time data.
## Load the library
```{r}
library(openskyr)
```
## Get state vectors
Get data with authentication in the REST API service:
```{r}
state_vectors_df = get_state_vectors()
state_vectors_df
```
Get data with authentication in the REST API service:
```{r, eval=NOT_CRAN }
state_vectors_df <- get_state_vectors(username="test_api_user",password="Test_Api_User")
head(state_vectors_df)
```
## Get airport data


## Get flights data


## Get tracks data


## More Examples

